\documentclass[11pt,oneside,letterpaper]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\usepackage{longtable}
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\newenvironment{packed_enumerate}{ %custom enumerate for single-spacing
\vspace{-7mm}
\begin{enumerate}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}
\vspace{-8mm}}

\begin{document}

\title{\bfseries PolitiMap: \\User Stories, Use Cases, and Requirements\\
Version 1.1}
\author{Matthew Goodrich}


\maketitle \thispagestyle{empty}

\pagebreak
\tableofcontents
\pagebreak

\newpage

\section{User Stories}
\subsection{Informing New Voters}
As a new voter, I want to be able to view previously-passed bills, so I can understand how politics have evolved and develop context for future bills.

\subsection{Customer Value}
As a busy voter, I want to be able to quickly view the status of new bills, so I can stay updated with politics, without investing too much of my valuable time.

\subsection{The Bigger Picture}
As an out-of-state student, I am affected by politics in multiple areas, meaning I want to be able to browse only federal bills and representatives, so I can invest my time well and only view relevant information.

\section{Unique Use Case}
\subsection{\label{Sim Data}Viewing Federal Bills}
\begin{longtable}{|r|p{3.8in}|}
\hline
Use Case ID:&1\\
\hline
Use Case Name:&View Federal Bills\\
\hline
Created By:&Matthew Goodrich\\
\hline
Last Updated By:&Matthew Goodrich\\
\hline
Date Created:&October 6, 2016\\
\hline
Date Last Updated:&October 6, 2016\\
\hline
Actors:&The Application User; The Swift iOS Application; The Backend Server\\
\hline
Description:&The application shall display a list of federal bills and further information about each upon selection.\\
\hline
Preconditions:&
\begin{packed_enumerate}
\item The device is connected to the internet.
\item The backend is loaded with the organized data.
\item The device has the application downloaded, updated, and open to the home screen.
\item The backend server is running, whether it be an AWS component or EC2 instance.
\end{packed_enumerate}\\
\hline
Postconditions:&
\begin{packed_enumerate}
\item A list of federal bills will be shown and likely scrolled-down, or the details of a specific bill will be showing.
\item A request will have been made to the AWS component or EC2 instance.
\item TBD - The federal bills may be cached in the user's device.
\end{packed_enumerate}\\
\hline
Normal Flow:&
\begin{packed_enumerate}
\item The user chooses to view the list of bills relating to their local, state, and federal governments.
\item A GET request is made to the web server while the user sees a loading animation.
\item The user selects to filter the list of bills to show only federal bills.
\item The user scrolls through the bills and notices an interesting one.
\item The interesting bill is selected and the user reads related information, including a summary, associated representatives, and links to related external documentation.
\end{packed_enumerate}\\
\hline
Alternative Flows:&
\begin{packed_enumerate}
\item The user selects a federal bills list instead of filtering a combined list.
\item The bills are loaded upon opening the application and only refreshed manually.
\item The bill information does not include associated representatives.
\item The bill shows dynamic data, such as votes and comments.
\end{packed_enumerate}\\
\hline
Exceptions:&
\begin{packed_enumerate}
\item Unable to load the bills through the lack of an internet connection.
\end{packed_enumerate}\\
\hline
Includes:&
\begin{packed_enumerate}
\item An external library to make the GET request.
\end{packed_enumerate}\\
\hline
Priority:&High - One of the core functions of the application.\\
\hline
Frequency of Use:&Depends on the number of users and other variables.\\
\hline
Business Rules:&None\\
\hline
Special Requirements:&
\begin{packed_enumerate}
\item The application requests the data asynchronously.
\item The device is an iPhone 5 or newer.
\item Specific bill information is loaded with a GET request after a bill is selected.
\end{packed_enumerate}\\
\hline
Assumptions::&
\begin{packed_enumerate}
\item Viewable federal bills exist in the backend.
\item Representatives have been linked to associated bills.
\item Documentation links have been added to associated bills.
\end{packed_enumerate}\\
\hline
Notes and Issues:&None\\
\hline
\end{longtable}

\section{Functional Requirements}
\subsection{Frequent Request Cost}
The system shall store the frequently accessed data, such as the list of federal bills, in AWS S3, to minimize the cost to \$.004 per 10,000 requests.

\subsection{Network Refresh}
The system shall refresh the list of federal bills from GET requests through a network connection.

\subsection{Default Bill Sorting}
The system shall default to sorting bills by the timestamp of their last update in content.

\section{Non-Functional Requirements}
\subsection{Quick Loading}
The system shall load the list of bills in under two seconds.

\subsection{Well-Developed iOS Application}
The system shall have zero memory leaks.

\subsection{Current Information}
Federal bills shall be updated within one day of receiving new information.

\end{document}